---
title: "Analytics Project - Prediction"
author: "Roli Srivastava"
date: "September 29, 2018"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
##Loading data and library files
```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn=-1) #  supress code warnings
#load required libraries
download.file("http://www.openintro.org/stat/data/nc.RData", destfile = "nc.RData")
load("nc.RData")
list.of.packages <- c("tidyverse", "knitr", "moments")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) 
  install.packages(new.packages, repos = "http://cran.us.r-project.org")
library(tidyverse)
library(knitr)
library(moments)
vgsale <-read.csv('C:/MyData/TerryMoonClass/Project/videogamesales/vgsales.csv',header= T)
salesData = vgsale
```


```{r}
Mode <- function(x) {
    if (is.numeric(x)) {
        x_table <- table(x)
        return(as.numeric(names(x_table)[which.max(x_table)]))
    }
}

```

* **Note**
      + The dataset file (*vgsales.csv*)and RMarkdown code/script need to co-exist in same directory for successful execution of this script.
      + DataSet Source: https://www.kaggle.com/kedokedokedo/vgsales

```{r exploratory analysis}
# Histogram to show the most popular platform
Platform <- data.frame(table(vgsale$Platform))
Platform$Percentage_Change <- (Platform$Freq/nrow(vgsale))*100


ggplot(Platform, aes(x = reorder(Platform$Var1, Platform$Percentage_Change), y = Platform$Percentage_Change))+
  labs(title = "Platform wise popularity" , x= "Platform",y= "Percentage")+
  geom_bar(stat="identity" , fill = "red")+
   coord_flip() 

## Genre wise Analysis
summary(vgsale$Genre)

# Histogram to show the most popular genre
Genre <- data.frame(table(vgsale$Genre))
Genre$Percentage_Change <- (Genre$Freq/nrow(vgsale))*100

ggplot(Genre, aes(x = reorder(Genre$Var1, Genre$Percentage_Change), y = Genre$Percentage_Change))+
  labs(title = "Genre wise popularity" , x= "Genre",y= "Percentage")+
  geom_bar(stat="identity" , fill = "black")+
   coord_flip() 

## Sale to count ratio > revenue sale per game
best_genre <- vgsale %>% subset(Genre != "Misc")  %>% select(Genre ,Name, Global_Sales) %>% group_by(Genre) %>%
summarise(count = n() , sales = sum(Global_Sales)) %>% arrange(desc(count))
best_genre$sales_count_Ratio <- round(best_genre$sales / best_genre$count , 2)
kable(best_genre)

## revenue sale Genre wise
ggplot(best_genre, aes(x = reorder(best_genre$Genre,best_genre$sales), y = best_genre$sales))+
  labs(title = "Revenue sale genre wise" , x= "Genre",y= "global sale")+
  geom_bar(stat="identity" , fill = "purple")+
   coord_flip() 

## revenue sale genre wise is Action , sports , shooter , role-playing , platform

## revenue sale per game
ggplot(best_genre, aes(x = reorder(best_genre$Genre,best_genre$sales_count_Ratio), y = best_genre$sales_count_Ratio))+
  labs(title = "Revenue sale per game" , x= "Genre",y= "sale count ratio")+
  geom_bar(stat="identity" , fill = "purple")+
   coord_flip() 

# revenue sale per game is Platform , shooter , role-playing , racing , sports

# Histogram to show the most popular top 10 publisher of the games
Publisher <- data.frame(table(vgsale$Publisher))
Publisher <- subset(Publisher , Publisher$Freq >=400)
kable(Publisher)

Publisher$Percentage_Change <- (Publisher$Freq/nrow(vgsale))*100
ggplot(Publisher, aes(x = reorder(Publisher$Var1, Publisher$Percentage_Change), y = Publisher$Percentage_Change))+
  labs(title = "Publisher wise popularity" , x= "Publisher",y= "Percentage_Change")+
  geom_bar(stat="identity" , fill = "green")+
   coord_flip() 


gameshare <- group_by(vgsale,vgsale$Year)
gameshare <- summarize(gameshare,World=sum(Global_Sales),NA.=sum(NA_Sales),EU=sum(EU_Sales),JP=sum(JP_Sales),Other=sum(Other_Sales))



cor(gameshare$NA.,gameshare$World)
cor(gameshare$EU,gameshare$World)
cor(gameshare$JP,gameshare$World)

#positive correlation between NA , EU , JP sale of games vs global sales of game , when NA , EU ,JP sale increases so is global sale of games
pairs(gameshare[,2:3])




## Region wise Total Sales
x <- c("World" ,"NA.","EU","Japan","Other")
y <- c(sum(gameshare$World) , sum(gameshare$NA.), sum(gameshare$EU), sum(gameshare$JP), sum(gameshare$Other))
gameV <- data.frame(x,y)

kable(gameV)
ggplot(gameV , aes(x,y))+
  labs(title = "Region wise Total Sales" , x= "Region",y= "Sales")+
  geom_bar(stat="identity" , fill = "pink")

## year-region wise sale from year 2000 - 2020
yearwise <- vgsale
yearwise <- within(yearwise, {
  YearSale <- as.numeric(as.vector.factor(yearwise$Year))})
  yearwise <- subset(yearwise ,yearwise$YearSale >= 2000)
ggplot(yearwise , aes(yearwise$YearSale,yearwise$NA_Sales))+
  labs(title = "Year wise Total Sales 2000-2020" , x= "Year",y= "Sales")+
  geom_bar(stat="identity" , fill = "blue")+
   coord_flip() 

## 1.Calculate a 95% confidence interval for the average NA Sales and interpret it in context.

inference(y = vgsale$NA_Sales, est = "mean", type = "ci", null = 0, conflevel = 0.95 ,
          alternative = "twosided", method = "theoretical")

## 1.Calculate a 95% confidence interval for the average Europe Sales and interpret it in context.

inference(y = vgsale$EU_Sales, est = "mean", type = "ci", null = 0, conflevel = 0.95 ,
          alternative = "twosided", method = "theoretical")

## 1.Calculate a 95% confidence interval for the average Japan Sales and interpret it in context.

inference(y = vgsale$JP_Sales, est = "mean", type = "ci", null = 0, conflevel = 0.95 ,
          alternative = "twosided", method = "theoretical")

## 1.Calculate a 95% confidence interval for the average Global Sales and interpret it in context.

inference(y = vgsale$Global_Sales, est = "mean", type = "ci", null = 0, conflevel = 0.95 ,
          alternative = "twosided", method = "theoretical")

inference(y = vgsale$Global_Sales, x = vgsale$Genre, est = "mean", type = "ht", null = 0, alternative = "greater", method = "theoretical")

```

## Descriptive analysis for global sale

```{r echo=FALSE}
##
##
dataD <- vgsale$Global_Sales
mnQ = mean(dataD)
modeQ = Mode(dataD)
mdQ = median(dataD)
sDQ= sd(dataD)
variQ = var(dataD)
kurQ= kurtosis(dataD)
skeQ= skewness(dataD)
maxQ= max(dataD)
minQ= min(dataD)
rangeQ = maxQ - minQ
sumQ = sum(dataD)
countQ = length(dataD)
qualitydata <- matrix(c(mnQ,modeQ,mdQ,sDQ,variQ,kurQ,skeQ,maxQ,minQ,rangeQ,sumQ,countQ),ncol =1 ,byrow = TRUE)
rownames(qualitydata) <- c('mean','mode','median','sd','var','kurtosis','skewness','max','min','range','sum','Count')
qualitydata <- as.table(qualitydata)
kable(qualitydata)

plot(vgsale$Platform ,vgsale$Global_Sales)

```

## Linear equation for global sale on Genre wise

```{r}

m1 <- lm(Global_Sales ~ Genre, data = vgsale)
summary(m1)
sum(m1$residuals^2) 
plot(vgsale$Global_Sales ,vgsale$Genre)
abline(m1)
## R-squared:  0.01194 
 
## Y = Global_Sales , X = Genre -(X0 = Action = 0 , Xa = Adventure , Xb =Fighting , Xc = Misc , Xd = Platform , xe = Puzzle , Xf = Racing , Xg = Role-Playing, Xh = Shooter , Xi = Simulation , Xj = Sports , Xk = Strategy )
## Y =  0.528100 - 0.342221 * Xa + 0.001275 * Xb - 0.062338 * Xc  + 0.410241 * Xd - 0.107224 * Xe  +  0.058001 * Xf + 0.095132 * Xg + 0.263785 * Xh - 0.075736 * Xi+  0.039219 * Xj - 0.270949 * Xk
## So Breakdown is 0 and running late is 1 
## for Action genre -  Y(Global sale) =  0.528100
## for Adventure genre-  Y(Global sale) = 0.528100 - 0.342221 * 1 =  0.185879
## so on and so forth

m1 <- lm(Global_Sales ~ Platform, data = vgsale)
m1 <- lm(Global_Sales ~ Publisher, data = vgsale)
```

##Market-wise Regression, ANNOVA & Prediction Analysis

###For North America (NA) Market

First, we build a multiple linear regression model.
```{r modelingNA}
#Subsetting the sales data to create a data frame with just NA sales and relevant independant variables
naSales <- salesData[, c("Platform", "Genre", "NA_Sales")]
#Studying the first few rows of the data frame
head(naSales, 10)
#Removing outliers from the codewith the 1.5 times the Inter Quartile range (IQR) rule
naSalesNoOutlier <- filter(naSales, NA_Sales <= (quantile(naSales$NA_Sales, 0.75) + (1.5 * IQR(naSales$NA_Sales))), NA_Sales >= (quantile(naSales$NA_Sales, 0.25) - (1.5 * IQR(naSales$NA_Sales))))
#Creating a multiple regression model
modelNA <- lm(NA_Sales ~ Platform + Genre, data = naSalesNoOutlier)
#Creating an ANOVA analysis
modelNA.aov <- aov(NA_Sales ~ Platform + Genre, data = naSales)
```

Next comes displaying the results of the regression analysis.
```{r resultsNA}
#Displaying the output of the multiple linear regression
summary(modelNA)
#Displaying the reidual plots
plot(modelNA)
#Displaying results of ANOVA analysis
summary(modelNA.aov)
```

Prediction a NA sales (in million units) for a particular platform and genre.
```{r predictNA}
predict(modelNA, data.frame(Platform = "PS3", Genre = "Shooter"))
```

###For European (EU) Market

First, we build a multiple linear regression model.
```{r modelingEU}
#Subsetting the sales data to create a data frame with just EU sales and relevant independant variables
euSales <- salesData[, c("Platform", "Genre", "EU_Sales")]
#Studying the first few rows of the data frame
head(euSales, 10)
#Removing outliers from the codewith the 1.5 times the Inter Quartile range (IQR) rule
euSalesNoOutlier <- filter(euSales, EU_Sales <= (quantile(euSales$EU_Sales, 0.75) + (1.5 * IQR(euSales$EU_Sales))), EU_Sales >= (quantile(euSales$EU_Sales, 0.25) - (1.5 * IQR(euSales$EU_Sales))))
#Creating a multiple regression model
modelEU <- lm(EU_Sales ~ Platform + Genre, data = euSalesNoOutlier)
#Creating an ANOVA analysis
modelEU.aov <- aov(EU_Sales ~ Platform + Genre, data = euSales)
```

Next comes displaying the results of the regression analysis.
```{r resultsEU}
#Displaying the output of the multiple linear regression
summary(modelEU)
#Displaying the reidual plots
plot(modelEU)
#Displaying results of ANOVA analysis
summary(modelEU.aov)
```

Prediction a NA sales (in million units) for a particular platform and genre.
```{r predictEU}
predict(modelNA, data.frame(Platform = "PS4", Genre = "Platform"))
```

###For Japanese (JP) Market

First, we build a multiple linear regression model.
```{r modelingJP}
#Subsetting the sales data to create a data frame with just JP sales and relevant independant variables
jpSales <- salesData[, c("Platform", "Genre", "JP_Sales")]
#Studying the first few rows of the data frame
head(jpSales, 10)
#Removing outliers from the codewith the 1.5 times the Inter Quartile range (IQR) rule
jpSalesNoOutlier <- filter(jpSales, JP_Sales <= (quantile(jpSales$JP_Sales, 0.75) + (1.5 * IQR(jpSales$JP_Sales))), JP_Sales >= (quantile(jpSales$JP_Sales, 0.25) - (1.5 * IQR(jpSales$JP_Sales))))
#Creating a multiple regression model
modelJP <- lm(JP_Sales ~ Platform + Genre, data = jpSalesNoOutlier)
#Creating an ANOVA analysis
modelJP.aov <- aov(JP_Sales ~ Platform + Genre, data = jpSales)
```

Next comes displaying the results of the regression analysis.
```{r resultsJP}
#Displaying the output of the multiple linear regression
summary(modelJP)
#Displaying the reidual plots
plot(modelJP)

#Displaying results of ANOVA analysis
summary(modelJP.aov)
```

Prediction a NA sales (in million units) for a particular platform and genre.
```{r predictJP}
predict(modelJP, data.frame(Platform = "PS3", Genre = "Shooter"))
```

##For Global (GB) Market

First, we build a multiple linear regression model.
```{r modelingGB}
#Subsetting the sales data to create a data frame with just GB sales and relevant independant variables
gbSales <- salesData[, c("Platform", "Genre", "Global_Sales")]
#Studying the first few rows of the data frame
head(gbSales, 10)
#Removing outliers from the codewith the 1.5 times the Inter Quartile range (IQR) rule
gbSalesNoOutlier <- filter(gbSales, Global_Sales <= (quantile(gbSales$Global_Sales, 0.75) + (1.5 * IQR(gbSales$Global_Sales))), Global_Sales >= (quantile(gbSales$Global_Sales, 0.25) - (1.5 * IQR(gbSales$Global_Sales))))
#Creating a multiple regression model
modelGB <- lm(Global_Sales ~ Platform + Genre, data = gbSalesNoOutlier)
#Creating an ANOVA analysis
modelGB.aov <- aov(Global_Sales ~ Platform + Genre, data = gbSales)
```

Next comes displaying the results of the regression analysis.
```{r resultsGB}
#Displaying the output of the multiple linear regression
summary(modelGB)
#Displaying the reidual plots
plot(modelGB)
#Displaying results of ANOVA analysis
summary(modelGB.aov)
```

Prediction a NA sales (in million units) for a particular platform and genre.
```{r predictGB}
predict(modelGB, data.frame(Platform = "PS3", Genre = "Shooter"))
```